 
% Letter class
\documentclass[10pt]{letter}

% Name of sender
%\name{Joe Fox}

% Signature of sender
%\signature{Joe Fox}

% Address of sender
%\address
%{
%    Fox Books,\\
%    Times Square, NYC.
%}

%-----------------------------------------------------------------------------%

\pagenumbering{gobble}
\begin{document}
\thispagestyle{empty}
% Name and address of receiver
\begin{letter}
% Opening statement
%\opening{Dear Ava,}

Ava,

It seems like not long ago I was driving my little girl to middle school, 
then to high school and making her listen to Bloomberg on the way.
I don't miss driving, but I do miss those little times we had to 
talk or joke or just be together.  Now you are driving yourself,
but thankfully I still get to see you in the morning.

  I am so proud of the giving, caring, loving, spiritual and intelligent young woman you have become.
As much as I want you to have those attributes I also know that it is mostly from 
within and from God that you draw your inspiration to be who you are.
And I am very proud of who you are. You are a your own person who 
 thinks for herself but always thinks of others.

You are a good example for others to follow.
   You work very hard in school and in your volunteer activities.
You give of yourself in all your relationships. 
You are a loving sister, daughter and pet mom to cocoa and we appreciate all you do for us.
Other people notice how special you are and sometimes say that we must have done a good job
raising you. I tell them all that while we tried to be good parents, it is mostly you 
who are responsible for the wonderful person you have become.

As we move through your senior year we start to think of the next steps for you.
I know you are working on your college applications and I know that if I were 
to see an application like yours I would stamp it accepted.
It's also a time when we think about what to do after school.
With your passion, intelligence and drive you can succeed at many things.
And you might end up doing some different things in your life, most people do and that is 
perfectly fine.  
At any time feel free to ask for advice.  I might even give 
some unsolicited advice at times so be patient with me.

This is a new phase of life for all of us. It can seem to  be a little scary, 
I don't want to think of not having you in the house every day.
But we have nothing to fear for it is really a wonderful time 
as you continue showing the world what you have to offer.
You have already shown us all so much.
The world can't wait to see how you grow and flourish, 
and neither can I.

Know that I will always love you unconditionally and support you in whatever you do.

Keep growing and Keep giving.

Love,

 \hspace{0.2in}  Dad



% Closing statement
%\closing{Yours truly,}

\end{letter}
\end{document}
