\documentclass{article}    
\usepackage[english]{babel}
\usepackage{enumitem}
                          

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}


\begin{document}

\noindent
I am a computer scientist and data scientist with over 20 years of experience in areas such as:
\begin{itemize}[noitemsep]
 \item algorithm design and implementation,
 \item analytics \& data science, and
 \item data visualization.
\end{itemize}

I have worked on a variety of application domains including image compression, retail forecasting, retail banking, risk management, asset management and most recently recommendation systems.

I have coded applications in C++, Java, Fortran, and Matlab but for most or my recent work I have used the Python ecosystem with SQL and occasionally R.
\vspace{0.1in}

Below is a sample of some of the Data Science, Machine Learning or AI projects I have worked on.
 \setlist{nolistsep}
\begin{itemize}[noitemsep]
\itemsep0em
\item Personal projects
    \begin{itemize}
  \item  Predicting the number of jobs added in the US.
  \item Analysis of voting data from the 2020 election, Georgia.
     \item Analysis of Asset Manager holdings, using SEC 13-F filings.
 \end{itemize}
 \item Part of online coursework:
    \begin{itemize}
       \item  Image recognition.
       \item Search tree algorithm for games, Pacman.
       \item Collaborative filtering for recommendations.
       \item Matrix Factorization for recommendations.
\end{itemize}        
\item  Consulting
 \begin{itemize}
     \item Clustering survey responses to find “natural” groupings.
     \item Survival Analysis for customer attrition.
      \item Predicting failures in oil equipment.    
  \end{itemize}       
\end{itemize}

%Other topics I am actively exploring are: Hidden Markov Models, Causal %Models and Machine learning for graph data.   \linebreak     
\vspace{0.1in}
Due to health issues starting in 2018 my career was sidetracked, hence the gap in my resume.
I am happy to say that I have rebounded. In 2021 I organized an online seminar through Deeplearning.ai, \emph{Migrating to Deep Learning},
to explore/discuss how technical people with experience in Data Science can get started in Deep Learning.


I am currently working through the Stanford online courses that are part of the AI certificate.  In 2021 I did the AI course.  
At the start of 2022 I did the graph ML course and moved on to the ML course.  I hope to follow up soon with either the Reinforcement Learning or the Natural Language Processing course.

\vspace{0.1in}
\begin{center}
\textbf{\emph{I am  looking for a role where I can apply and  continue to develop \\
my skills in computer science and data science}}
\end{center}.
\vspace{0.1in}

\noindent I would love to speak with someone about how I could contribute to your organization.
Best regards,
John Muller

\end{document}