\documentclass{article}    
\usepackage[english]{babel}
\usepackage{enumitem}
                          

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}


\begin{document}

\noindent
I am a computer scientist and data scientist with over 20 years of experience in areas such as:
\begin{itemize}[noitemsep]
 \item algorithm design and implementation,
 \item analytics \& data science, and
 \item data visualization.
\end{itemize}

I have over 10 years of experience in quant equity investing.
On the sell side I worked for State Street Associates which is part of State Street's trading divistion.
On the buy side I worked for Acadian Asset Management as well as a short stint 
  in the corporate investments group at Bank of America.
  
I have coded applications in C++, Java, Fortran, and Matlab but for most or my recent work I have used the Python ecosystem with SQL and occasionally R.
\vspace{0.1in}


    
\vspace{0.1in}
Due to health issues starting in 2018 my career was sidetracked, hence the gap in my resume.
I am happy to say that I have rebounded. In 2021 I organized an online seminar through Deeplearning.ai, \emph{Migrating to Deep Learning},
to explore/discuss how technical people with experience in Data Science can get started in Deep Learning.


In 2022 I completed courses to earn the AI certificate from Stanford.
The courses included AI, Graph ML and Machine Learning.  

\vspace{0.1in}
\begin{center}
\textbf{\emph{I am  looking for a role where I can apply and  continue to develop \\
my skills in computer science, data science and quantitative finance}}
\end{center}.
\vspace{0.1in}

\noindent I would love to speak with someone about how I could contribute to your organization.\\
Best regards,

John Muller

\end{document}