% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}
{\LARGE \underline{John Muller}}
\vspace{0.1in}
\hfill\break
\textbf{email}: jmuller.ics88@gtalumni.org \\
\textbf{phone}:  (704) 593-6855\\
\textbf{LinkedIn}: https://www.linkedin.com/in/quantjohn/\\
\textbf{Address}: 17823 Meadow Bottom Rd., Charlotte, NC USA 28277\\
\textbf{Github}: http://github.com/\textbf{\emph{jhmuller}} \\
%\textbf{website}: www.enterthedata.com \\

\hypertarget{summary}{%
\section{\texorpdfstring{\underline{\textbf{Summary}}}{Summary}}\label{summary}}

\begin{itemize}
\tightlist
\item
  Computer Scientist, Data Scientist, and Finance Quant.
\item
  Extensive experience with

  \begin{itemize}
  \tightlist
  \item
    Python ecosystem, machine learning frameworks, SQL and R.
  \item
    Algorithms, Data Structures, Data Science, and visualization.
  \end{itemize}
\item
  Academic training in machine learning, big data methods and
  quantitative finance.
\end{itemize}

% \line(1,0){4in} 

\hypertarget{professional-experience}{\section{\texorpdfstring{\underline{\textbf{Professional
Experience}}}{Professional Experience}}\label{professional-experience}}

\hypertarget{lowes}
{\subsubsection{} \label{lowes}}

\begin{flushleft}
\textbf{Company} : Lowe's Digital Data Science 
\end{flushleft}

\begin{flushleft}
\textbf{Role} : Data Scientist
\end{flushleft}
{\textbf{From}: Nov 2021 \hspace{0.5in}  \textbf{To}: April 2022}
\begin{itemize}
\tightlist
\item
  Part of a team building and deploying recommendation algorithms.
\item
  Built both a rules-based method from counts derived from web logs as
  well as a graph ML model using PyTorch Geometric.
\item
  Built a tool to create an HTML document for manual comparison of any
  number of competing recommendation methods.
\item
  Proposed a system for \emph{offline back testing} of recommendation
  algorithms.
\end{itemize}


%\line(1,0){.5in} 
\hypertarget{pnc}{\subsubsection{}\label{pnc}}
\begin{flushleft}
\textbf{Company} : PNC Bank
\end{flushleft}

\begin{flushleft}
\textbf{Role} : Python code review lead
\end{flushleft}

\textbf{From}: Oct 2019 \hspace{0.5in} \textbf{To}: Oct 2021

Part of code review team, responsibilities included:

\begin{itemize}
\tightlist
\item
  Reviewing Python and SQL code and ensuring code runs and produces
  desired output,
\item
  Determining if code accurately and completely meets documented
  requirements.
\end{itemize}
Required skill in and knowledge of Python, SQL, Spark, Hadoop and Hive.


%\line(1,0){.5in} 
\hypertarget{acadian}{\subsubsection{}\label{acadian}}
\begin{flushleft}
\textbf{Company} : Acadian Asset Management
\end{flushleft}

\begin{flushleft}
\textbf{Role} : Analytics and Python coding lead
\end{flushleft}

\textbf{From}: Feb 2013 \hspace{0.5in}  \textbf{To}: Mar 2018\\

\begin{itemize}
\tightlist
\item
  Designed and built a Dashboard for Portfolio Managers to analyze
  portfolio exposures within and across strategies.
\item
  Rebuilt from scratch a module to orthogonalize one signal to other
  factors/signals.
\item
  Developed code to add transaction costs to our attribution and a web
  app (Bokeh) for exploring the results.
\item
  Built an automatic testing program to run simple pass/fail tests on
  code where no explicit test code exists. Used Python's introspection
  to find methods and method signatures to assign valid values for
  arguments.
\item
  Developed a Python version of the R Corrgram method for re-ordering
  the rows and columns of a correlation matrix to help reveal clusters
  of related variables.
\item
  Other projects Included:

  \begin{itemize}
  \tightlist
  \item
    Investment strategy capacity analysis,
  \item
    Rebalancing schedule frequency analysis,
  \item
    Rranking of broker performance,
  \item
    FX hedge reporting module,
  \item
    Access layer to alpha model data, and more.
  \end{itemize}
\end{itemize}

%\line(1,0){.5in} 
\hypertarget{enterthedata}{\subsubsection{}\label{enterthedata}}
\begin{flushleft}
\textbf{Company}: Enter The Data
\end{flushleft}
{\hspace{.1in} \footnotesize \emph{EnterTheData is my own consulting firm.}}
\begin{flushleft}
\textbf{Role}: Data Scientist
\end{flushleft}

\textbf{From}: Feb 2012 \hspace{0.5in}  \textbf{To}: Feb 2013\\
Descriptive and predictive modeling, visualization and data science
consulting. Projects included:

\begin{itemize}
\tightlist
\item
  Estimating the value of a marketing campaign vis-à-vis resulting sales
  using time series analysis,
\item
  Analyzing customer retention using survival analysis to find
  differences across markets,
\item
  Estimating weather effects on sales,
\item
  Predicting government employment releases using lasso regression and
  random forests.
\end{itemize}

%\line(1,0){.5in} 
\hypertarget{ssa}{%
\subsubsection{}\label{ssa}}
\begin{flushleft}
\textbf{Company} : State Street Associates
\end{flushleft}

{\hspace{0.1in} \footnotesize \emph{State Street Associates is the research arm of State Street Corporation's trading business.}}


\begin{flushleft}
\textbf{Role} : Analytics and Sell side research lead
\end{flushleft}

\textbf{From}: Aug 2007 \hspace{0.5in}  \textbf{To}: Feb 2012 \\

 

  \begin{itemize}
  \tightlist
  \item
    Created back-end database structure combining internal and external
    data sources.
  \item
    Created a front-end trader dashboard, using Spotfire, to serve as
    the trader's main information portal.
  \item
    Analysis and modeling including: predicting hard-to-borrow
    securities and analyzing the relationship between real and synthetic
    shorts using options.

  \item
    Team leader for new holdings indicators, i.e. trading signals, for
    equity and fixed income.
  \item
    Team leader and active participant in research and development of
    the equity holdings indicator.
  \item
    Managed teams that developed and released 14 new Foreign Exchange
    and Equity flow indicators.
  \end{itemize}
%\end{itemize}

%\line(1,0){.5in} 

\hypertarget{bofa}{\subsubsection{}\label{bofa}}
\begin{flushleft}
\textbf{Company} : Bank of America
\end{flushleft}

\begin{flushleft}
\textbf{Role} : Analytics lead
\end{flushleft}
\textbf{From}: Oct 2001 \hspace{0.5in}  \textbf{To}: Aug 2007\\

  \begin{itemize}
  \tightlist
  \item
    Coding (using R) and back-testing various improvements to the
    existing momentum-style strategy drawing data from MarketQA, IDC,
    IBES, and Compustat.
  \item
    Quantitative support for users of Barra's Enterprise Performance
    product for return attribution.

  \item  Provided quantitative support for managing the banks institutional loan portfolio.
  \item
    Designed and coded fixed income tools using R and C++.
  \item
    Developed code to calculate Nelson-Siegel curves and bond asset swap
    spreads.

  \item   Conducted extensive analysis of customer database and provided
  analytic research on the effects of pricing policies to support the
  mortgage pricing team. 
  \item Used statistical techniques to analyze
  loan-level cash flow data and build models to predict servicing
  profitability based on borrower
  \end{itemize}
%\end{itemize}

\emph{Contact me for earlier work history.}

\hypertarget{education-and-activities}{
\section{\texorpdfstring{\underline{\textbf{Education and
Activities}}}{Education and Activities}}\label{education-and-activities}}

\hypertarget{university-education}{%
{\large \textbf{University Education}}\label{university-education}}

\textbf{Degree}: Doctor of Philosophy,  Ph.D.\\
\textbf{Major}: Information and Computer Science \\
\textbf{Institution}: Georgia Institute of Technology\\
\vspace{0.1in}

\textbf{Degree}: Bachelor of Science, B.S. \\
\textbf{Major}: Computer Science \\
\textbf{Institution}: University of Georgia

\hypertarget{continuing-education-and-related-activities}{%
{\large \textbf{Continuing Education and related
activities}}
\label{continuing-education-and-related-activities}}

\begin{itemize}
\tightlist
\item
  Artificial Intelligence Professional Program, Stanford University

  \begin{itemize}
  \tightlist
  \item
    Machine Learning, XCS229, (2022)
  \item
    Machine Learning with Graphs, XCS224, (2022)
  \item
    Artificial Intelligence: Principals and Techniques, XCS221, (2021)
  \end{itemize}
\item
  DeepLearning.ai courses including Neural Networks and Deep Learning
  and Sequence Models (2018)
\item
  Data Science: Data to Insights and Big Data, MIT professional
  development online course (2017)
\item
  Statistical Learning and Data Mining III, Elements of Statistical
  Learning authors Tibshirani \& Hastie (2011)
\item
  Co-founder and current co-organizer of Greater Boston useR Meetup
  Group (2900+ Members) (2010)
\item
  Certificates in Quantitative Finance, Stanford (2005), Carnegie Mellon
  (2006)\\
  Courses Included: Finance, Statistics and Mathematics, Stochastic
  Calculus, and Interest Rate Models.
\end{itemize}

\end{document}
