% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{pagecolor,lipsum}% http://ctan.org/pkg/{pagecolor,lipsum}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}
\usepackage{lipsum}
\usepackage{titlesec}
\titlespacing\section{0pt}{2pt plus 4pt minus 2pt}{0pt plus 0pt minus 2pt}
\titlespacing\subsection{0pt}{0pt plus 0pt minus 0pt}{0pt plus 0pt minus 2pt}

\begin{document}
%\pagecolor{CornflowerBlue}
{\LARGE \underline{John Muller}}
\vspace{0.1in}
\hfill\break
jmuller.ics88@gtalumni.org $\diamondsuit$  (617) 669-2204  $\diamondsuit$  Charlotte, NC USA 28277\\
https://www.linkedin.com/in/quantjohn/ $\diamondsuit$ http://github.com/jhmuller/jhmuller.github.io \\

\vspace{-18pt}

\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}

%\hypertarget{summary}{%
%\section{\texorpdfstring{\underline{\textbf{Summary}}}{Summary}}\label{summary}}
\vspace{-2pt}
\begin{itemize}
\item  Computer Scientist(Ph.D.), Data Scientist, and Finance Quant with over 15 years of experience solving analytic problems in a variety of industries.
\item Loves understanding the big picture and working with the clients and stakeholders to define and then execute on solutions that add value. 
%{\textbf {Technical Skills}}
\item Technical skills
  \begin{itemize}
	\tightlist
	\item Python and it's ecosystem: notebooks, pandas, numpy, et cetera 
	\item scikit learn, keras/tensoflow,and pytorch.
	\item Skill and experience with ML algorithms ranging from regression to ensemble methods to neural networks.
 \end{itemize}
\end{itemize}
 
% \line(1,0){4in} 
\vspace{6pt}
\hypertarget{professional-experience}{\section{\texorpdfstring{\underline{\textbf{Experience}}}{Professional Experience}}\label{professional-experience}}
\vspace{-16pt}
{\subsubsection{} \label{BofA}}
{\textbf {Bank of America \hfill  Python developer \hfill Nov. 2022 -- present}}

\begin{itemize}
\tightlist
\item Developing Python and SQL tools to give the bank a more flexible process for loading and managing sensitive data.
\end{itemize}

\vspace{-18pt}
{\subsubsection{} \label{enterthedata}}
{\textbf {Enter The Data \hfill  Data Scientist \hfill 2012 - present}}\\
\emph {My own brand for Data Science and Computer Science consulting}

\begin{itemize}
\tightlist
\item  Time series exploratory analysis and prediction.
\item Estimating the value of marketing campaigns to optimize marketing spend.
\item
  Analysis of customer churn to improve retention.
\item
  Analyzing and estimating the effects of weather on sales to optimize inventory.
\item Clustering using survey data.
\end{itemize}

\vspace{-18pt}
\hypertarget{lowes}
{\subsubsection{} \label{lowes}}

\textbf {Lowe's \hfill Data Scientist \hfill Nov 2021 - Apr 2022}\\
\vspace{-10pt}
\begin{itemize}
\tightlist
\item
  Coded a rules-based method for recommendations which was put into 
   production.
   
 \item  Built a machine learning
  method for generating recommendations that can use product attributes as well as web traffic data.  This was important because
  it addressed the issue of new products which have no 
    history of view data. 
\end{itemize}


\pagebreak

\hypertarget{pnc}{\subsubsection{}\label{pnc}}
\textbf  {PNC Bank \hfill Python Developer \& Code Reviewer \hfill Oct 2019 - Oct 2021}

\vspace{-2pt}

\begin{itemize}
\tightlist
\item Helped avoid Regulatory Penalties by reviewing over 24 sets of Python and SQL code to ensure that the code meets the requirements and is correct.
\item Developed a Pandas dataframe profiling tool
that produced an extensive summary of a dataframe  saving time 
for all reviewers.
\end{itemize}

\vspace{-16pt}
%\line(1,0){.5in} 
\hypertarget{acadian}{\subsubsection{}\label{acadian}}
\textbf {Acadian Asset Management \hfill Vice President \& Analyst \hfill  Feb 2013 -  Mar 2018}

\begin{itemize}
\tightlist
\item
 Designed and built a dashboard for Portfolio Managers to compare returns and exposures for sets of portfolios, 
 allowing them to identify both anomalies and opportunities in the portfolios.
\item
Implemented adding transaction costs
into the attribution framework given Portfolio Managers
a better understanding of it's effects on returns.
\item 
  Devised and developed  a method to estimate broker skill, based on page rank,  which can lead to  reducing trading costs.
\end{itemize}


\vspace{-18pt}
%\line(1,0){.5in} 
\hypertarget{ssa}{%
\subsubsection{}\label{ssa}}
\textbf {State Street Associates \hfill Vice President, Analyst and Visualization lead \hfill Aug 2007 - Feb 2012 }

\vspace{-4pt}
{\hspace{0.1in} \footnotesize \emph{State Street Associates is the research arm of State Street Corporation's trading business.}}

\vspace{-8pt}

  \begin{itemize}
  \tightlist
  \item
	Extensive modeling on both equity 
    and securities lending in order to create Investor Behavior indicators 
    for both asset classes.

  \item Team leader for the group responsible 
    for creating both the Fixed income and equity holdings indicators.
    \item Managed teams that developed and released 14 new Foreign Exchange and Equity flow indicators.
  \item Built a
  dashboard for the Sec Lending traders that unified their data 
  allowed for new kinds of comparison and analysis.
   Once complete it was put into use on the desk immediately.    
  \end{itemize}
%\end{itemize}

%\line(1,0){.5in} 

\hypertarget{bofa}{\subsubsection{}\label{bofa}}
\textbf {Bank of America \hfill Senior Vice President \hfill Oct 2001 -  Aug 2007}

  \begin{itemize}
  \tightlist
  \item
	Coded and back-testing methods for low frequency automated trading of equities based on momentum strategies.
  \item
   While in Risk Management, to support a project on revising the loan hedging strategies, I developed tools to analyze differences in rate on corporate bonds with the same rating to support 

  \item Analyzed loan-level cash flow data and build models to predict     mortgage servicing profitability based on borrower attributes.
  \item Also while with the Consumer Real Estate group I 
    did extensive analysis on the effects of pricing policies 
    in support of the mortgage pricing team. 
  \end{itemize}
%\end{itemize}

\emph{Contact me for earlier work history.}

\hypertarget{education-and-activities}{
\section{\texorpdfstring{\underline{\textbf{Education and
Activities}}}{Education and Activities}}\label{education-and-activities}}

\hypertarget{university-education}{%
{\large \textbf{University Education}}\label{university-education}}

\textbf{Degree}: Doctor of Philosophy,  Ph.D.\\
\textbf{Major}: Information and Computer Science \\
\textbf{Institution}: Georgia Institute of Technology\\
\vspace{0.1in}

\textbf{Degree}: Bachelor of Science, B.S. \\
\textbf{Major}: Computer Science \\
\textbf{Institution}: University of Georgia

\hypertarget{continuing-education-and-related-activities}{%
{\large \textbf{Continuing Education and related
activities}}
\label{continuing-education-and-related-activities}}

\begin{itemize}
\tightlist
\item
  Artificial Intelligence Professional Program, Stanford University

  \begin{itemize}
  \tightlist
  \item
    Machine Learning, XCS229, (2022)
  \item
    Machine Learning with Graphs, XCS224, (2022)
  \item
    Artificial Intelligence: Principals and Techniques, XCS221, (2021)
  \end{itemize}
\item
  DeepLearning.ai courses including Neural Networks and Deep Learning
  and Sequence Models (2018)
\end{itemize}

\end{document}
