\documentclass{letter}    
\usepackage[english]{babel}
\usepackage{enumitem}
                          

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}
\usepackage[skip=10pt plus1pt, indent=40pt]{parskip}

\begin{document}

\noindent
I am a \textbf {computer scientist, data scientist and finance quant} with years of experience 
in areas such as:
\vspace{-.1in}
\begin{itemize}[noitemsep]
 \item quantitative finance, 
 \item analytics, data science, \& data visualization, and
 \item algorithm design \& implementation,
\end{itemize}

\noindent I have worked on a variety of application domains 
(e.g. image compression, retail forecasting and more)
but my favorite application areas are market related.

\noindent I find the problems in markets and trading fascinating in that they often require thinking in terms of finance, economics, behavior, math, statistics, et cetera.
In addition, finding good solutions is rewarding in many ways.


I find that sports analytics has many of the features that I like about markets.  Constructing fantasy teams is like creating a portfolio.  Predicting performance in sports in similar to predicting alpha in a stock.
Also just as in the market, many participants arrive with their own unique constraints, opinions and models.
I think working in this area would be very interesting and rewarding and I believe I would have a lot to offer.
 

\noindent
I would love to speak with someone there about how I could bring all of my skills and experience \\
to contribute to your organization.

\vspace*{0.2in}
\noindent Best regards,\\
John Muller

\end{document}