\documentclass{letter}    
\usepackage[english]{babel}
\usepackage{enumitem}
                          

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}
\usepackage[skip=10pt plus1pt, indent=40pt]{parskip}

\begin{document}

\noindent
I am a \textbf {computer scientist, data scientist and finance quant} with years of experience 
in areas such as:
\vspace{-.1in}
\begin{itemize}[noitemsep]
 \item quantitative finance, 
 \item analytics, data science, \& data visualization, and
 \item algorithm design \& implementation,
\end{itemize}

\noindent I have worked on a variety of application domains 
(e.g. image compression, retail forecasting and more)
but my favorite application areas are market related.

\noindent I find the problems in markets and trading fascinating in that they often require thinking in terms of finance, economics, behavior, math, statistics, et cetera.
In addition, finding good solutions is rewarding in many ways.


\noindent
I had the pleasure of working on market related 
problems at Bank of America, State Street and Acadian Asset Management.
\begin{itemize}
\item Bank of America: I worked in the Corporate Investments team on momentum based quantitative strategies.

\item State Street: I was in the Investor Behavior team 
 creating signals from State Street's eauity and securities lending custody data.
 I also worked with the Securities Lending team to create a dashboard for the traders.
 
\item Acadian: I worked both in the Portfolio Construction team as well as the Implementation team. I worked on issues such as trading frequency, strategy capacity and prime broker ranking. I also worked on signals and bringing new model code into production.
 \end{itemize}
 

\noindent
While I do not have industry experience in high-frequency trading I am keenly interested in the area and I think my skills and experience would prove extremely valuable.

\noindent
I am proficient in Python.  I used to code in C/C++ but it has been a while.  I used Matlab at State Street and SAS at BofA.

\noindent
I would love to speak with someone at Towers about how I could bring all of my skills and experience \\
to contribute to your organization.

\vspace*{0.2in}
\noindent Best regards,\\
John Muller

\end{document}